Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
some results work

All simulations were run with in a domain $8.192\times
10^4~\mathrm{cm} \times 2.048\times 10^4~\mathrm{cm}$.  With our
default refinement, this gives a resolution of $20~\mathrm{cm}$ on the
finest level.  As a comparison, the resolution in our detonation
models was $98~\mathrm{cm}$ and in our multidimensional convection
studies was $6~\mathrm{cm}$.

We specify the rotation period, $P_\mathrm{rot}$, which is related to
the angular rotation rate as $\Omega = 2\pi / P_\mathrm{rot}$.  Our
default rotation period is $0.0005~\mathrm{s}$ (2000 times per
second).  This is quite fast, but picked to make the Rossby length
small enough to fit in the spatial scales we can model.  With this
rotation rate, the Rossby length is
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
\MarginPar{we should make the width of the hot region closer to the
  Rossby length} using a scale height $H_0 = 10^3~\mathrm{cm}$.  This
is less than half our domain width.  Table~\ref{table:sim_names} lists
the simulations run and their parameters.

We note that the entire simulation framework for these calculations is
freely available in the \castro\ github repository\footnote{\url{https://github.com/AMReX-Astro/Castro}}.

>>>>

Table~\ref{table:sim_names} summarizes the simulations that we ran.
The majority of them used a reaction rate boosting of $10$ and a
conductivity boosting of $10$, which should increase the flame speed
by a factor of $10$.  Most simulations used a resolution of
$10~\mbox{cm}$ and a domain width of a little more than one kilometer.  
We use an artifically high rotation rate of
$2000~\mbox{Hz}$, which gives a Rossby length of
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
using a scale height $H_0 = 10^3~\mathrm{cm}$.  This is about one
quarter of domain width.  The run at $20~\mbox{cm}$ resolution used
one fewer level of refinement.  The slower rotating case using a
slightly wider domain to accommodate the expected larger Rossby
length.  We note that the entire simulation framework for these
calculations is freely available in the \castro\ github
repository\footnote{\url{https://github.com/AMReX-Astro/Castro}}.
